Codebook created on 2021-01-31 at 2021-01-31 09:51:38

### 2021-01-31 codebook_df.Rmd
remove derived variables

---
title: "Codebook created on 2021-01-31 at 2021-01-31 09:50:03"
output: github_document
---

@@

## Dataset description
The data contains 1904 cases and 27 variables.

>>>>

---
title: "Codebook created on 2021-01-31 at 2021-01-31 09:51:38"
output: github_document
---

@@

## Dataset description
The data contains 1904 cases and 21 variables.
